### 2015-06-26 texfiles/manuscript.tex
First commit

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref,booktabs,multirow,cleveref,pdflscape}
\modulolinenumbers[5]

\journal{Environmental Software and Modeling}

\bibliographystyle{APA-style}\biboptions{authoryear}

\begin{document}

\begin{frontmatter}

\title{Resource Alignment Service and Its Application in Envisioning the Model Web}

\author[address]{Peishi Jiang}
\author[address]{Mostafa Elag}
\author[address]{Praveen Kumar\corref{correspondingauthor}}

\cortext[correspondingauthor]{Corresponding author}
\ead{kumar1@illinois.edu}

\address[address]{Ven Te Chow, Hydrosystem Laboratory, Civil and Environmental Engineering, University of Illinois, Urbana, USA}

\begin{abstract}
Development of integrated Geoscience system increasingly requires the coupling multidisciplinary models and integration between data and models. Many Geoscience communities have adopted an approach of disseminating their models over the web, which are known as Model as a Service (MaaS). The web serviced models can be easily (re)used, accessed, and extended. Furthermore, the concept of Model Web has been recently proposed to describe a service-oriented architecture in coupling web serviced models. To envision a world of Model Web, one of the key challenges is to ensure the semantic interoperability of serviced models. To address this need, we put forward Semantically-Enabled Modles (SEM) where the information of a web serviced model is enriched by adding a semantic layer on the model, and designed the Resource Alignment Service (RAS) to ensure the semantic consistency between information exchanged between SEMs. In this paper, we first present the designs of SEM and RAS, and then demonstrate RAS application for both semantic coupling serviced models and integration of serviced models and data. A workflow of heterogeneous collection of web serviced data and models is created. Finally, we show how the semantic interoperability issue in coupling SEMs can be solved by utilizing RAS.
\end{abstract}

\begin{keyword}
Model Web \sep Semantic Interoperability \sep Resource Alignment Service (RAS) \sep Semantically-Enabled Model (SEM) 
\end{keyword}

\end{frontmatter}

\linenumbers

\section{Introduction}For decades, integrated environmental modeling has been applied in investigating the mechanism of the entire ecosystem, which becomes increasingly complex under climate change and human impact recently \citep{argent2004, laniak2013}. With the growing efforts in integrated modeling, scientists with a solo discipline background are able to access, reuse and couple resources (i.e., models and data) from various disciplines. It therefore enhances their assessment, prediction and management abilities of a complicated natural system. One of the approaches is through envisioning a world of “Model Web”, where the functionalities of models are exposed through web services and these resources are integrated via the internet \citep{geller2007, geller2008, nativi2013}. Hence, one of the challenges facing the community is to achieve the “minimal barriers to entry” \citep{nativi2013} or the interoperability between the serviced resources. In this study, we aim to propose a mechanism ensuring the semantic consistency of information flowing among serviced-oriented modeling.

The application of service-oriented architecture in environmental modeling just starts recently \citep{castronova2013, mineter2003, granell2010, goodall2011, goodall2013}. Following the concept of Software as a Service (SaaS), models and data can also be exposed as web services, called as Model as a Service (MaaS) and Data as a Service (DaaS), respectively. MaaS or DaaS are able to exchange data with other serviced models over the web, implying a loose-coupling approach of model integration \citep{goodall2011}. It is different from the traditional integrated modeling approach through tight coupling, where the initial independent models are coupled under a modeling integration application or framework. The representative integration frameworks include the Community Surface Dynamics Modeling System (CSDMS), Earth System Modeling Framework (ESMF), OpenMI standard and so forth \citep{hill2004, peckham2013, moore2005}. The advantage of the tight-coupling approach is that the framework entirely controls both the data structures and processes of all parts of the model. Nevertheless, due to the fixed convention or standard of a framework, it is difficult to couple models not following the standard or conventions. On the contrary, through the service-oriented loose-coupling approach, only the uniform protocol of data exchanging is required \citep{goodall2011}. It allows individual model developers or groups to maintain and update their models conveniently.

To achieve a world of interoperable serviced models and data, the concept of “Model Web” was put forward by \citep{geller2008}. Later, Nativi explicitly defined it as “a dynamic web of models, integrated with databases and websites, to form a consultative infrastructure where researches, managers, policy makers, and the general public can go to gain insight into ‘what if’ questions” in initiating it under the project of the Group on Earth Observation” \citep{nativi2013}. Several efforts have been made to draw the picture of “Model Web”. \citet{goodall2011} exposed water resource models as web services through Web Processing Service (WPS) and demonstrated how it could be encapsulated as OpenMI-compliant models. Then, they furthered the idea of servicing an OpenMI-compliant model based on WPS by considering the case of time-dependent models \citep{castronova2013}. Furthermore, an OpenMI-ESMF web service wrapper was developed to couple a climate model implemented via ESMF web service with an OpenMI-compliant hydrologic model running on a personal computer \citep{goodall2013}.\\
One of the key technical challenges in envisioning “Model Web” is to achieve the “minimal interoperability agreement” between serviced resources \citep{nativi2013}. It requires both a uniform protocol for communication and the semantic consistency of quantities exchanging between services.

Without it, semantics is one of the impediments to consumption and reuse of online heterogeneous or long-tail resources \citep{elag2015} as shown in Figure \ref{figure1}. The semantic consistency requirements include: (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) temporal alignment of resource time horizon and (4) spatial alignment of resources spatial attributes. The existing efforts described in the previous paragraph try to achieve such interoperability by applying a specific standard. For instance, apply OpenMI standard in integrating water resource models serviced by WPS \citep{goodall2011, castronova2013}. Nevertheless, the application of a certain standard or framework might not be fruitful. This is because the existence of different standards or frameworks in different domains might imply the adoption of a specific framework in one discipline, thus complicating the online communication of serviced resources from various disciplines. For example, an OpenMI-compliant serviced model cannot talk with a serviced model embedded in Object Modeling System (OMS, \cite{david2013}) without a proper wrapper for communication between OpenMI and OMS. Furthermore, standards like OpenMI do not allow semantic mediation between variable names, prohibiting the integration of models with variables in alias names.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{../figures/figure_1.eps}
\label{figure1}
\caption{Semantics as the impediments for scientists, data consumers and web applications to integrating heterogeneous or long-tail resources over the web.}
\end{figure}

To tackle the issue of semantic interoperability of integrating service-oriented modeling, we introduce the Semantically-Enabled Model (SEM) by adding a semantic layer on top of a serviced model or MaaS, and then utilize a Web service named Resource Alignment Service (RAS) to align the quantities exchanging between SEM over the web. As a product of GeoSemantic framework, which aims to overcome the semantic heterogeneity among long-tail models an data collections \citep{elag2015}, RAS is designed as a metadata-agnostic Web service for the geoscience communities in order to ensure the semantic consistency of information transferred between serviced resources via the internet in terms of the name, unit, and temporal and spatial properties of variable.

In the remainder of the paper, Section 2 describes the general idea and the main components of GeoSemantic framework and the roles of SEMand RAS playing in it. In Section 3, the entire architecture of achieving the semantic interoperability in coupling serviced models is presented, including the designs of both SEM and RAS. Section 4 demonstrates the application of RAS in coupling SEMs and integration of SEM and data. First we create a workflow of heterogeneous collection of data and SEM. Then, we show how RAS can seamlessly align the semantics of quantities exchanging between these resources. Finally, a brief summary is given in Section 5, with mentions on the future work.

\section{GeoSemantic Framework}GeoSemantic framework is an ongoing project that aims to allow the structured information seamlessly exchanging between various resources by achieving their semantic interoperability \citep{elag2015}. Through semantic web technology \citep{berners2001}, GeoSemantic enhances the capability of finding resources by searching a standard names graph, discovering the implicit relationships between resources by reasoning, and annotating a new or an existing resource by adding semantic tags.

As shown in Figure \ref{figure2}, to enable the search, annotation and discovery capability described above, a standard names graph is set up in a Jena TDB \footnote{https://jena.apache.org/documentation/tdb/} triple store,  to collect the linked vocabularies containing various standard names (SN), with four web services provided allowing users to fully utilize the functionality offered by GeoSemantic. The Knowledge Integration Service (KIS) imports the annotated standard names (e.g., CSDMS standard names \citep{peckham2014CSN}, the controlled vocabulary of observations data model \citep{horsburgh2009}, ingesting their thesaurus, and updates them into the GeoSemantics Wiki (a wiki describing the relationship between different standard names) and the triple store. The Knowledge Discovery Service (KDS) conducts semantic search and finds required resource in the triple store. The Semantic Annotation Service (SAS) annotates the metadata of resources in online repository (e.g., Clowder, an online resource collections developed under GeoSemantics framework). And the Resource Alignment Service (RAS) ensures the semantic consistency of information flowing between either serviced models (e.g., SEM) or a serviced model and serviced dataset (e.g.,  Clowder). In this study, we focus on the utilization of RAS on integration of SEMs to help envisioning the “Model Web”.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.3]{../figures/figure_2}
\label{figure2}
\caption{The architecture of GeoSemantic framework. Four web services (i.e., KIS, KDS, SAS and RAS) are developed to allow users to import or ingest the standard names into the triple store, discover the inherent relationships between the resources from the triple store, annotate metadata of resources semantically and align two heterogeneous resources. In this study, we focus on the application of RAS in coupling SEM to envision the Model Web.}
\end{figure}

\section{Methodology}In this section, we present the architecture of how to ensure the semantic interoperability of serviced models as shown in Figure \ref{figure3}. To add a semantic layer on top of the available or new web serviced models, SEM is put forward by creating a dynamic metadata schema for processing these serviced models with minimum hum interventions. Then, RAS  is applied to ensure and do the required semantic alignment between the fields of the metadata schema of the relevant models in terms of (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) conversion of different file types; (4) temporal alignment of resources time horizon; (5) spatial alignment of resources spatial attributes.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.4]{../figures/figure_3}
\label{figure3}
\caption{The functionality of RAS in aligning the input and outputs of the serviced models.}
\end{figure}

\subsection{Semantically-Enabled Model(SEM)}The objective of SEM is to put a semantic layer on top of a serviced model to allow the external features of the model available and processable for other service like RAS. The models are exposed as services through the Open Geospatial Consortium (OGC) Web Processing Service (WPS). WPS is utilized because it provides a standard for processing data \citep{schut2007opengis}, which has proven to be successfully applied in other modeling study requiring data exchanging between services \citep{castronova2013, goodall2011, schaeffer2008,vitolo2012}.

As depicted in the design of SEM in Figure \ref{figure4}, the semantic layer of SEM is added by creating a dynamic metadata schema based on a specified variable template in JSON format, which describes the name, the unit, the type, and the tempo-spatial properties of variable. The JSON-based metadata of a web serviced model includes not only the inputs and outputs but also the Uniform Resource Identifier (URI) for model execution. The metadata is assumed to live with the model codes in a same remote server and be serviced as well. It means the metadata of SEM is also available through an HTTP GET, with a different URI but the same namespace compared with the URI for the model execution through WPS.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.4]{../figures/figure_4}
\label{figure4}
\caption{Design of Semantically-Enabled Model (SEM) with a variable template example for \textit{Rainfall}.}
\end{figure}

To completely contain information of a variable used in a model, the basic elements of the JSON-based variable template include:

\paragraph{variableName} It illustrates the name of variable, with two keys: \textit{value} and \textit{type}. The field of type could be either “uri” or “string”, which indicates the field of \textit{value} as a URI or a simple string, respectively.

\paragraph{unit} It illustrates the unit of variable, with two keys: \textit{value} and \textit{type} functioning same as those of \textit{variableName}.

\paragraph{variableType} It illustrates the value, data and file type of variable in keys \textit{valueType}, \textit{storageType} and \textit{fileExtension}, respectively. The basic value types include integer, float, double, boolean, string and so forth. The field of storageType contains “singleValue” (a single value), “list” (a list of values) and “matrix” (a matrix of values). And the file type is detailed in \textit{fileExtension} (e.g., “.csv” for the Comma Separated Values (CSV) file, “.nc” for the Network Common Data Form (netCDF) file). Furthermore, to allow RAS be aware of where to store or pick up the data file, two other keys are added in \textit{variableType}: \textit{storagePath} and \textit{pickupPath}, with URIs as fields indicating the location of the file. Furthermore, \textit{storagePahHead} and \textit{pickupPathHead} indicate the headers of the data in the files with \textit{storagePath} and \textit{pickupPath}, respectively, if any.

\paragraph{timeHorizon} It illustrates the temporal property of variable, with keys: \textit{start}, \textit{end} and \textit{step}. \textit{start} and \textit{end} are the start and end time of variable used in the model. Both of them have two keys: \textit{value} and \textit{format}, where format indicates the format or standard (e.g., ISO8601) of the field of \textit{value}. If the start and end times are not required by the model, the fields of value of \textit{start} and \textit{end} are entered as “notSpecified”.  Moreover, \textit{step} describes the time step of variable, with information of time step value and time step unit (e.g., “h” for hour, “min” for minute) stored in keys \textit{value} and \textit{unit}.

\paragraph{spatialProperty} It illustrates the spatial property of variable, with keys: \textit{boundaries}, \textit{LatStep}, \textit{LonStep} and \textit{gridType}. \textit{boundaries} contains the boundaries of variable, stored either in a bounding box (with key \textit{boundingBox}) or a shape file (with key \textit{shapeFile}). The latitude and longitude resolutions of variable are depicted in \textit{LatStep} and \textit{LonStep} with keys \textit{value} and \textit{unit}. Finally, the type of grid (e.g., uniform, rectilinear) is described in \textit{gridType}.

It should be noted that if variable used in a model does not have any information for an attribute (key), the field of it is entered as “None”. For example, for a time series of rainfall at a specified location, the fields of all keys in \textit{spatialProperty} should be escaped as “None”.

\subsection{Resource Alignment Service (RAS)} RAS is developed as a service to ensure the semantic consistency of information exchanging between online resources. The entire functionality of it includes semantic mediation of variable names, conversion of mismatched units and file type, and tempo-spatial alignment. A Python web application package, Flask\footnote{http://flask.pocoo.org/}, is utilized to set up the service. In this study, it is applied to align quantities flowing between SEM.

\subsubsection{RAS Architecture}As shown in Figure \ref{figure5}, RAS is a web service allowing the alignment between two list variables in terms of: variable name, variable unit, variable value type, file type, variable temporal and spatial properties. The alignment is carried out for each pair of variables, say, aligning from variable I to variable II.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.4]{../figures/figure_5}
\label{figure5}
\caption{The architecture of the Resource Alignment Service (RAS).}
\end{figure}

\paragraph{variable name} The semantic mediation of two variable names is conducted through either a SKOS-based search or a string-based search. SKOS-based search is applied for variable names in a form of URI. The procedures of it are (1) finding all the matched (i.e., \textit{skos:exactMatch} or \textit{skos:closeMatch}) variable names for variable I by querying the standard names graph through SPARQL\footnote{http://www.w3.org/TR/rdf-sparql-query/}, an Resource Description Framework (RDF) query language; (2) checking whether variable II is in the list of the matched variables of variable I (return matched if true). \textit{rdflib}\footnote{https://github.com/RDFLib/rdflib}, a Python library for working with RDF, is utilized for RDF querying. In addition, if the types of variable names are string, then the mediation is through string-based search. The variable name in string is first transformed in a URI format by assigning it with a model name space. Then SKOS-based search is used for semantic mediation.

\paragraph{variable unit} Similar to the alignment of two variable names, the conversion of two variable units is based on \textit{natu} conversion and SWEET unit conversion, according to the types of units: string and URI, respectively. If the unit types are string, a Python unit conversion package, \textit{natu}\footnote{http://kdavies4.github.io/natu/} (Natural units in Python), is employed to perform the conversion. On the other hand, SWEET unit ontology is applied in the case that both the unit formats are URI.

\paragraph{variable type} The alignment of the variable types of two variables is based on both the value and file types conversion. The value type alignment is straightforward through type conversion in Python (e.g., from \textit{float} to \textit{integer}). In terms of conversion in file types, currently the supported file types are csv/txt, xls and.nc, with the header information in the file if any.

\paragraph{variable time horizon} The temporal property alignment of two variables is conducted through linear temporal interpolation, given the start time, the end time and the time step of each variable. By temporal interpolation approach, the actual time period of the data of variable II aligned from that of variable I is the intersection of the given time periods of the two variables. It means if the time periods (from the start time to the end time) of the two variables do not overlap, there is no data interpolated for variable II.

\paragraph{variable spatial property} The alignment of two variables’ spatial property is carried out through regridding and projection. Based on the boundary and grid information of two variables, regridding is utilized for spatial interpolation from grids of variable I to those of variable II. Also, projection, or map projection is a transformation from the latitudes and longitudes of locations on earth of a sphere into grids or locations in a plane. This functionality is still under development.

\subsubsection{RAS Functionality} The purpose of RAS is to avoid the semantic mismatch of two variable lists by aligning each pair of variables through the functions described in Section 2.2.1. Generally, through HTTP POST method, the service takes the metadata of the two variables lists, along with the values of a list of variables, in JSON format. For example, to apply RAS to ensure that the output(s) of a SEM (say, SEM I) can be utilized as the input(s) of another SEM (say, SEM II), the following information is required to be fed into RAS: 
\begin{itemize}
\item the metadata of the output(s) of SEM I
\item the output values of SEM I
\item the metadata of the input(s) of SEM II
\end{itemize}
Then, the process of the semantic check and the alignment happens inside of the RAS service based on the alignment functions for the different properties (i.e., name, unit, type, time horizon and spatial property). In the case of alignment between input and output of two SEMs, the process is conducted based on the metadata of the two SEMs, which is introduced in Section 3.1. Once the alignment process finishes, the values of the other variable list, aligned from the provided values of the first list, is returned 262 in JSON format.

In addition, it should be noted that for each pair of variables, the alignment would fail in the cases of the following situations:
\begin{itemize}
\item the two variable names are mismatched through either SKOS-based or string-based search
\item the storage types of the two variables are not the same (e.g., one is a single value, another is a list of values).
\end{itemize}

\section{Application} Two applications are presented: (1) serviced data-model integration (DaaS $\rightarrow$ MaaS) and (2) serviced model-model integration (DaaS $\rightarrow$ MaaS $\rightarrow$ MaaS). All the MaaS are deployed as SEMs and RAS is utilized for ensuring the semantic interoperability between serviced resources.  In the first application, DaaS $\rightarrow$ MaaS, meteorological data stored Clowder is aligned to the format of the inputs of a SEM-based Priest-Taylor model through RAS. In the application of DaaS $\rightarrow$ MaaS $\rightarrow$ MaaS, RAS is used for the alignment between both the data from Clowder and the output of Priest-Taylor model and a SEM-based 1D Richard equation model.

\subsection{DaaS and MaaS in Application} 
\subsubsection{SEMs in Application} The Priestley-Taylor approach is an approach for estimating evaporation at areas with low moisture stress, a modification of Penman’ approach for evaporation estimation \citep{priestley1972}. It requires information of net short wave and long wave radiation, ground heat flux and air temperature at a specific location. In this study, the ground heat flux is generated from a linear relationship between it and soil temperatures at different levels.

Richards’ equation, developed by \cite{richards1931}, simulates the water movement process in unsaturated soils. Given the time series information of evaporation and precipitation, Richard’s equation is able to generate the profiles of both the soil pressure head and the soil moisture over time by solving its non-linear partial differential equation. In this study, 1D Richards equation is utilized in the application, which simplifies the whole process by considering the vertical direction.

Both the models are serviced through PyWPS\footnote{http://pywps.wald.intevation.org/}, a Python implementation of WPS. The original codes of the two models are in Python and MATLAB for Priest-Taylor and 1D Richard equation, respectively. To allow the MATLAB-based 1D Richard equation model serviced by PyWPS, the package, MATLAB Engine for Python \footnote{http://www.mathworks.com/help/matlab/matlab-engine-for-python.html}, is used to enable calling MATLAB code from Python. Also, the JSON-based metadata of the two models, of which the example is provided in Figure \ref{figure4}, are also serviced and available through HTTP GET request, which is set up by Flask.

\subsubsection{Clowder} In addition, Clowder, as a product of GeoSemantic framework, is developed as an online resource (i.e., model and data) repository allowing resource upload, annotation and extraction of the metadata of the resource. Users can annotate or extract the metadata of a resource through either a web page interface or web service APIs. The metadata available for annotation includes temporal/spatial reference, description, variable name mapping, abstract and so forth. To feed the required inputs of the two models, the soil surface temperature, the net short and long wave radiation, the air temperature, the precipitation and the soil temperature at depth of 4 meter in 2007 at Bondville are uploaded and annotated in Clowderas 306 shown in Figure \ref{figure6}.

\begin{landscape}
\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.4]{../figures/figure_6}
\label{figure6}
\caption{The screenshots of the five environmental datasets at Bondville in 2007 uploaded to Clowder and the metadata of \textit{precipitation.csv} file.}
\end{figure}
\end{landscape}

\subsubsection{Relations and Heterogeneities among Data in Clowder and Variables in the two SEMs} Figure \ref{figure7} illustrates the relationships among the data stored in Clowder and the I/O of the two SEMs. In the first application (i.e., DaaS $\rightarrow$ MaaS), information stored in Clowder (i.e., the surface temperature, net long and short wave radiation, air temperature and soil temperature at depth of 4 meters at Bondville in 2007) is used for the input of the serviced Priest-Taylor model after a certain alignment through RAS. For the second application, the required inputs of 1D Richard equation are given by both the precipitation at Bondville in 2007 from Clowder and the evaporation output of the Priestley-Taylor model generated from the first application.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.4]{../figures/figure_7}
\label{figure7}
\caption{The relationships among the Bonville’s environmental data in 2007 from Clowder and the inputs and outputs of Priestley-Taylor model and 1D Richard equation.}
\end{figure}

In both applications, RAS is utilized to ensure the semantic consistency of quantities flowing from either Clowder or the SEM’s output to the inputs of the twoSEMs. The semantic heterogeneities of the data used in Clowderand the I/O of the two models are provided in Table \ref{tabel1}. It can be observed that the variables or data differ from each other in terms of name, unit, value type, file extension and time horizon properties. In terms of naming, the names of data from Clowder are defined with an underscore separating words while variable names in the two models are in format of camelCase. Units and file extension of variables are also different. For example, the unit of data “precipitation” in Clowder is in mm while the required unit of the input “Rainfall” in 1D Richard equation is in cm; the format of Priestley-Taylor model’s output (“LandSurfaceEvaporation”) is netCDF but the “Evaporation” of 1D Richard equation requires CSV file. For time horizon, we assume that both the Priestley-Taylor model and 1D Richard equation has the same fixed time range but with different time steps as 1h and 0.5h, respectively. The fixed time range of the two models is for differing from the period of time of data from Clowder which covers the whole year 2007.

\begin{landscape}
\begin{table}[h]
\small
\centering
\renewcommand{\arraystretch}{0.6}
\caption{The properties of the Clowder's data used in this study.}
\label{tabel1}
\begin{tabular}{*8c}
\toprule
Clowder&Name&Unit &Value type&File extension & Start time & End time & Time step                      \\
\midrule
\multirow{6}{*}{Data}&air\_temperature                      & degF        & double    & .csv  & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
					    	      &surface\_temperature               & degF       & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
							  &soil\_temp\_4m\_underground & degF        & double    & .csv  & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
							  &net\_longwave\_radiation         & W*m-2     & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
							  &net\_shortwave\_radiation       & W*m-2      & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
							  &precipitation                             & mm           & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h      \\
\midrule
Priestley-Taylor model&Name&Unit &Value type&File extension & Start time & End time & Time step                      \\
\midrule
\multirow{6}{*}{Input}&AirTemperature                     & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &NetLongwaveRadiation        & W*m-2   & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &NetShortwaveRadiation        & W*m-2  & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &SoilTempAtSurface               & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &SoilTempAtDepthOfXMeters & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &SoilDepthOfXMeters	           & m           & double    & /        & /								  & /								    & /      \\
Output                      &LandSurfaceEvaporation       & m           & double    & .nc     & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
\midrule
1D Richard equation&Name&Unit &Value type&File extension & Start time & End time & Time step                      \\
\midrule
\multirow{6}{*}{Input}&AirTemperature                     & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &NetLongwaveRadiation        & W*m-2   & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &NetShortwaveRadiation        & W*m-2  & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &SoilTempAtSurface               & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &SoilTempAtDepthOfXMeters & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
							  &SoilDepthOfXMeters	           & m           & double    & /        & /								  & /								    & /      \\
Output                      &LandSurfaceEvaporation       & m           & double    & .nc     & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

\subsection{Implementation} A workflow is created to carry out the coupling of heterogeneous data and models as presented in Figure \ref{figure7}. Basically, in the first application, based on the metadata of Priestley-Taylor model, data of \textit{air\_temperature}, \textit{surface\_temperature}, \textit{soil\_temperature\_underground}, \textit{net\_longwave\_radiation}  and \textit{net\_shortwave\_radiation} in Clowder is first aligned to the required semantics of the inputs of the Priestley-Taylor model by RAS. Then, once the input is ready, the model execution is conducted through a HTTP request to the WPS-based service. In the second application, RAS is used again to align from the output of Priestley-Taylor model and \textit{precipitation} data in Clowder to the two inputs of 1D Richard equation. The Richard equation execution is performed after the alignment.

To ensure the successful alignment through RAS, besides the utilization of the several conversion functions (e.g., unit conversion, temporal interpolation), a comprehensive standard names graph is also required for the semantic mediation of variable names. Figure \ref{figure8} shows how the variable names in Table \ref{tabel1} are related with each other by using SKOS. For example, \textit{AirTemperature} in Priestley-Taylor model is matched with \textit{air\_temperature} in Clowder based on their same \textit{skos:exactMatch} \textit{csn:atmosphere\_bottom\_air\_\_temperature}, a CSDMS standard name for describing air temperature at the bottom of the atmosphere.

\begin{landscape}
\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.3]{../figures/figure_8}
\label{figure8}
\caption{The SKOS-based relationships between CSDMS standard names and the variable names in the application stored in the standard names graph.}
\end{figure}
\end{landscape}

\section{Summary and Future Work} An approach for ensuring the semantic consistency of information exchanging between serviced resources was designed to help integrating serviced models. To solve the semantic interoperability issue in envisioning a world of Model Web, serviced models or MaaS were semantically enabled as SEM with the application of the Resource Alignment Service (RAS) in dealing with the semantic inconsistency of quantities exchanging between SEMs. To allow the external features (e.g., inputs and outputs) of a model available for other clients (e.g., users or services), Semantically-Enabled Models (SEM) were put forward by adding semantic layer on top of a serviced model and the Open Geospatial Consortium’s (OGC) Web Processing Service (WPS) standard was utilized as the data specification. Based on the semantic information of SEM, RAS was then applied to check and resolve the misalignment of two lists of variables in terms of names, units, value and file types, temporal and spatial properties.

A workflow of heterogeneous collection of serviced data and SEMs was created to show how RAS can seamlessly align the semantics of quantities exchanged between these resources. Priestley-Taylor model and 1D Richard equation were deployed as SEM serviced by PyWPS. Environmental data stored in Clowder was fed as inputs for the two models to create the workflow in a manner of DaaS $\rightarrow$ MaaS $\rightarrow$ MaaS as shown in Figure \ref{figure7}. The heterogeneities of data in Clowder and variables in the two models are presented in Table \ref{tabel1}. With the implementation shown in Section 4.2, we conclude that it is possible to resolve the semantic interoperability issue of coupling web serviced models by enhancing the semantic information for the model and using an alignment tool such as RAS to achieve reduce the semantic consistency.

Nevertheless, as RAS is still under development, the functionality of RAS can be enhanced in the following points. First, the functions for spatial alignment are required, which probably includes the regridding (an interpolation process from one grid to another grid) and projection (a transformation process from one coordinate system to another coordinate system). The OGC standards could provide a good option to record the spatial information of a variable used in a specific model with a specific tools conducting the spatial alignment, like ESMF Python Regridding Interface \footnote{https://www.earthsystemcog.org/projects/esmpy/}. Additionally, a more comprehensive file type conversion tool is required. Current file type conversion utility in RAS only supports CSV, Excel and netCDF files, with emphasis on tabular file format. Software like Polyglot \footnote{http://opensource.ncsa.illinois.edu/projects/POL}, a distributed service capable of file format conversions, might be a choice for conversion of more file types. Moreover, for structured file formats (e.g., netCDF, Gridded Binary (GRIB)), a simple header information is not enough for describing the required data content in the file despite of its current usage in the variable template for SEM. Therefore, instead of a specified header, an extra document describing the internal information of the data file could be better in providing the semantic information of the data in the file. For example, netCDF-LD, ''a convention for encoding netCDF based on Linked Data principles'' \citep{yu2015}, might be applied for enhancing the semantics of a netCDF file.

Finally, we here only try to solve the issue of the semantic interoperability in coupling serviced models. To envision the world of Model Web, more works are required to tackle the other technical challenges, as summarized by \cite{nativi2013}. One of them is the high performance challenges. The primary disadvantage of loosely-coupled, service-oriented modeling is that it might affect computation efficiency negatively when large datasets are required to transfer via the internet for the initialization or parameterization of the serviced models \cite{goodall2011}. Another challenge is related to the reliability or long term access of the services. The service might be unavailable for the users due to different reasons (e.g., the broken or updates of the remote server), thus disabling all the clients utilizing it. Issues described above need further investigations

\section*{Acknowledgement} The authors wish to acknowledge the auspice of NSF Grant Council (project numbers ICER 1440315, ACI 12-61582, ACI 0940824, and EAR-1331906) for the support of this study. The gratitude is also extended to Luigi Marini and Rui Liu from NCSA at the University of Illinois at Urbana-Champaign for their help and comments in deploying the service.

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2015-07-10 texfiles/manuscript.tex
Revise the first two sections.

@@
 
+\usepackage[margin=2.5cm]{geometry}
 \usepackage{lineno,hyperref,booktabs,multirow,cleveref,pdflscape}
@@
 
-\title{Resource Alignment Service and Its Application in Envisioning the Model Web}
+\title{Towards Decentralized Integration of Environmental Resources on the Web: A Resource Alignment Service}
 
-\author[address]{Peishi Jiang}
-\author[address]{Mostafa Elag}
-\author[address]{Praveen Kumar\corref{correspondingauthor}}
+\author[address1]{Peishi Jiang}
+\author[address1]{Mostafa Elag}
+\author[address2]{Luigi Marini}
+\author[address2]{Liu Rui}
+\author[address1]{Praveen Kumar\corref{correspondingauthor}}
 
@@
 
-\address[address]{Ven Te Chow, Hydrosystem Laboratory, Civil and Environmental Engineering, University of Illinois, Urbana, USA}
+\address[address1]{Ven Te Chow, Hydrosystem Laboratory, Civil and Environmental Engineering, University of Illinois, Urbana, IL, USA}
+\address[address2]{National Center for Supercomputing Applications, University of Illinois, Urbana, IL, USA}
 
 \begin{abstract}
-Development of integrated Geoscience system increasingly requires the coupling multidisciplinary models and integration between data and models.
-Many Geoscience communities have adopted an approach of disseminating their models over the web, which are known as Model as a Service (MaaS).
-The web serviced models can be easily (re)used, accessed, and extended.
-Furthermore, the concept of Model Web has been recently proposed to describe a service-oriented architecture in coupling web serviced models.
-To envision a world of Model Web, one of the key challenges is to ensure the semantic interoperability of serviced models.
-To address this need, we put forward Semantically-Enabled Modles (SEM) where the information of a web serviced model is enriched by adding a semantic layer on the model, and designed the Resource Alignment Service (RAS) to ensure the semantic consistency between information exchanged between SEMs.
-In this paper, we first present the designs of SEM and RAS, and then demonstrate RAS application for both semantic coupling serviced models and integration of serviced models and data.
-A workflow of heterogeneous collection of web serviced data and models is created.
-Finally, we show how the semantic interoperability issue in coupling SEMs can be solved by utilizing RAS.
+...
 \end{abstract}
@@
 \begin{keyword}
-Model Web \sep Semantic Interoperability \sep Resource Alignment Service (RAS) \sep Semantically-Enabled Model (SEM) 
+Model Web \sep semantic interoperability \sep the Resource Alignment Service (RAS) 
 \end{keyword}
@@
 \section{Introduction}For decades, integrated environmental modeling has been applied in investigating the mechanism of the entire ecosystem, which becomes increasingly complex under climate change and human impact recently \citep{argent2004, laniak2013}.
-With the growing efforts in integrated modeling, scientists with a solo discipline background are able to access, reuse and couple resources (i.e., models and data) from various disciplines.
+With the growing efforts in integrated modeling, scientists with a solo discipline background are able to access, reuse and couple reosurces (i.e.,  models and data) from various disciplines.
 It therefore enhances their assessment, prediction and management abilities of a complicated natural system.
-One of the approaches is through envisioning a world of “Model Web”, where the functionalities of models are exposed through web services and these resources are integrated via the internet \citep{geller2007, geller2008, nativi2013}.
-Hence, one of the challenges facing the community is to achieve the “minimal barriers to entry” \citep{nativi2013} or the interoperability between the serviced resources.
-In this study, we aim to propose a mechanism ensuring the semantic consistency of information flowing among serviced-oriented modeling.
+One of the approaches is through envisioning a world of ''Model Web'', where the functionalities of a model are exposed through web services and then integrated via the internet \citep{geller2007, geller2008, nativi2013}.
+As stated by \cite{nativi2013}, one of the challenges in achieving the web-serviced model integration is to ensure the 'minimal barriers to entry' or the interpoerability between the serviced resources.
+In this study, we aim to envision a world of 'Model Web' with emphasis on ensuring the semantic consistency of information flowing between web-serviced resources in geoscience.
 
 The application of service-oriented architecture in environmental modeling just starts recently \citep{castronova2013, mineter2003, granell2010, goodall2011, goodall2013}.
-Following the concept of Software as a Service (SaaS), models and data can also be exposed as web services, called as Model as a Service (MaaS) and Data as a Service (DaaS), respectively.
-MaaS or DaaS are able to exchange data with other serviced models over the web, implying a loose-coupling approach of model integration \citep{goodall2011}.
-It is different from the traditional integrated modeling approach through tight coupling, where the initial independent models are coupled under a modeling integration application or framework.
-The representative integration frameworks include the Community Surface Dynamics Modeling System (CSDMS), Earth System Modeling Framework (ESMF), OpenMI standard and so forth \citep{hill2004, peckham2013, moore2005}.
-The advantage of the tight-coupling approach is that the framework entirely controls both the data structures and processes of all parts of the model.
-Nevertheless, due to the fixed convention or standard of a framework, it is difficult to couple models not following the standard or conventions.
-On the contrary, through the service-oriented loose-coupling approach, only the uniform protocol of data exchanging is required \citep{goodall2011}.
-It allows individual model developers or groups to maintain and update their models conveniently.
+Folliwng the concept of Software as a Service (SaaS), models and data can also be exposed as web services, called as Model as a Serice (MaaS) and Data as a Service (DaaS), respectively.
+To achieve a world of interoperable MaaS and DaaS, the concept of ''Model Web'' was put forward by \citep{geller2008}.
+Later, \cite{nativi2013} explicitly defined it as ''a dynamic web of models, integrated with databases and websites, to form a consultative infrastructure where researches, managers, policy makers, and the general public can go to gain insight into ‘what if’ questions'' in initiating it under the project of the Group on Earth Observation.
+Several efforts have been made to draw the picture of “Model Web”.
+\citet{goodall2011} exposed water resource models as web services through the Open Geospatial Consortium (OGC) Web Processing Service (WPS) and demonstrated how it could be encapsulated as OpenMI(open modeling interface and environment)-compliant models.
+Then, they furthered the idea of servicing an OpenMI-compliant model based on WPS by considering the case of time-dependent models \citep{castronova2013}.
+Furthermore, an OpenMI-ESMF web service wrapper was developed to couple a climate model implemented via ESMF web service with an OpenMI-compliant hydrologic model running on a personal computer \citep{goodall2013}.
 
-To achieve a world of interoperable serviced models and data, the concept of “Model Web” was put forward by \citep{geller2008}.
-Later, Nativi explicitly defined it as “a dynamic web of models, integrated with databases and websites, to form a consultative infrastructure where researches, managers, policy makers, and the general public can go to gain insight into ‘what if’ questions” in initiating it under the project of the Group on Earth Observation” \citep{nativi2013}.
-Several efforts have been made to draw the picture of “Model Web”.
-\citet{goodall2011} exposed water resource models as web services through Web Processing Service (WPS) and demonstrated how it could be encapsulated as OpenMI-compliant models.
-Then, they furthered the idea of servicing an OpenMI-compliant model based on WPS by considering the case of time-dependent models \citep{castronova2013}.
-Furthermore, an OpenMI-ESMF web service wrapper was developed to couple a climate model implemented via ESMF web service with an OpenMI-compliant hydrologic model running on a personal computer \citep{goodall2013}.\\
-One of the key technical challenges in envisioning “Model Web” is to achieve the “minimal interoperability agreement” between serviced resources \citep{nativi2013}.
-It requires both a uniform protocol for communication and the semantic consistency of quantities exchanging between services.
-
-Without it, semantics is one of the impediments to consumption and reuse of online heterogeneous or long-tail resources \citep{elag2015} as shown in Figure \ref{figure1}.
-The semantic consistency requirements include: (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) temporal alignment of resource time horizon and (4) spatial alignment of resources spatial attributes.
+One of the key challenges in model integration communinity is the heterogeneity or long-tail property of models and data.
+Due to different habits of research groups or individual scientists, models developed by them would probably differ in operating system, programming language, variable name, data unit, temporal-spatial property and so forth.
+In the world of Model Web, a user of a web-serviced model does not need to consider the operating system or programming language of which the model is serviced and implemented because he or she only interacts with the exposed service.
+But the user is required to be aware of both the communication protocol the service applies and the remaining heterogeneities (e.g., variable name, data units).
+Otherwise, the semantic inconsistency of information flowing between services would impact the functionaility of a web serivce negatively as shown in \ref{semanticInconsistency}.
+To achieve a seamless integration of serviced resources, a uniform protocol and an aligning mechanism are required for information processing and ensuring reducing the semantic consistency of data flowing between serviced resources, respectively.
 The existing efforts described in the previous paragraph try to achieve such interoperability by applying a specific standard.
@@
 Nevertheless, the application of a certain standard or framework might not be fruitful.
-This is because the existence of different standards or frameworks in different domains might imply the adoption of a specific framework in one discipline, thus complicating the online communication of serviced resources from various disciplines.
+This is because the existence of different frameworks in different domains might imply the adoption of a specific framework in one discipline, thus complicating the online communication of serviced resources from various disciplines.
 For example, an OpenMI-compliant serviced model cannot talk with a serviced model embedded in Object Modeling System (OMS, \cite{david2013}) without a proper wrapper for communication between OpenMI and OMS.
@@
 \centering
-\includegraphics[scale=0.5]{../figures/figure_1.eps}
-\label{figure1}
-\caption{Semantics as the impediments for scientists, data consumers and web applications to integrating heterogeneous or long-tail resources over the web.}
+\includegraphics[scale=0.4]{../figures/figure_MaaS_misalignment.pdf}
+\label{semanticInconsistency}
+\caption{An illustration of the semantic inconsistency between two web serviced models.}
 \end{figure}
 
-To tackle the issue of semantic interoperability of integrating service-oriented modeling, we introduce the Semantically-Enabled Model (SEM) by adding a semantic layer on top of a serviced model or MaaS, and then utilize a Web service named Resource Alignment Service (RAS) to align the quantities exchanging between SEM over the web.
-As a product of GeoSemantic framework, which aims to overcome the semantic heterogeneity among long-tail models an data collections \citep{elag2015}, RAS is designed as a metadata-agnostic Web service for the geoscience communities in order to ensure the semantic consistency of information transferred between serviced resources via the internet in terms of the name, unit, and temporal and spatial properties of variable.
+To tackle the issue of semantic interoperability of integrating service-oriented modeling, we develop a web service named Resource Alignment Service (RAS) to ensure semantic consistency of information exchanged between MaaS over the web, including: (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) temporal alignment of resource time horizon and (4) spatial alignment of resources spatial attributes.
+Models are implemented by the WPS, which exposes both its execution and its inputs and outputs (I/O) properties through web service.
+Then, RAS is utilized to align the quantities exchanging between MaaS over the webthe two types of serviced models.
 
-In the remainder of the paper, Section 2 describes the general idea and the main components of GeoSemantic framework and the roles of SEMand RAS playing in it.
-In Section 3, the entire architecture of achieving the semantic interoperability in coupling serviced models is presented, including the designs of both SEM and RAS.
-Section 4 demonstrates the application of RAS in coupling SEMs and integration of SEM and data.
-First we create a workflow of heterogeneous collection of data and SEM.
+In the remainder of the paper, Section 2 describes the design requirement and provides a short overview on model integration community.
+In Section 3, the architecture of the Resource Alignment Service (RAS is presented, including the an brief overview of GeoSemantic framework, the functionality and the components of RAS.
+Section 4 demonstrates the application of RAS in coupling WPS-implemented models with the input data from Clowder, an online data repository.
+First we create a workflow of heterogeneous collection of data and WPS-implemented models.
 Then, we show how RAS can seamlessly align the semantics of quantities exchanging between these resources.
@@
 
-\section{GeoSemantic Framework}GeoSemantic framework is an ongoing project that aims to allow the structured information seamlessly exchanging between various resources by achieving their semantic interoperability \citep{elag2015}.
-Through semantic web technology \citep{berners2001}, GeoSemantic enhances the capability of finding resources by searching a standard names graph, discovering the implicit relationships between resources by reasoning, and annotating a new or an existing resource by adding semantic tags.
+\section{Design Requirement and Overview}
+Modeling integration in geoscience has advanced significantly these years because of the increasing collaboration between scientists or research groups from various disciplines (e.g., hydrology, geology, ecology and so on).
+The traditional integrated modeling approach is through tight coupling, where the initial independent models are coupled under a modeling integration application or framework.
+The representative integration frameworks include the Community Surface Dynamics Modeling System (CSDMS), Earth System Modeling Framework (ESMF), OpenMI standard and so forth \citep{hill2004, peckham2013, moore2005}.
+The CSDMS architecture employs the component-based modeling approach, where standand-alone models are encapsulated and coulped with others in a plug-and-play manner.
+For each model, a BMI (Basic Model Interface) file is required for recording the model's basic information and converting it into a plug-and-play component.
+Then, the integration process is conducted in the Component Model Interface based on all the utilities provided by CSDMS frameowork.
+ESMF is aimed at coupling models from Earth science (e.g., wearther and climate model), with a 'sandwich' pattern characterizing its architecture \citep{hill2004}.
+The user code layer contains all the model components in ESMF, which are then encapsulated in the superstructure layer aligning and connecting the input and output data between models.
+All the utilities for the alignment are provided in the infrastructure layer.
+In addition, OpenMI is an effort on model coupling in water resource community.
+It provides a standard interface for any new or existing models exchanging data with each other during running period.
+Now the OpenMI standard is adopted as a specification in the OGC.
 
-As shown in Figure \ref{figure2}, to enable the search, annotation and discovery capability described above, a standard names graph is set up in a Jena TDB \footnote{https://jena.apache.org/documentation/tdb/} triple store,  to collect the linked vocabularies containing various standard names (SN), with four web services provided allowing users to fully utilize the functionality offered by GeoSemantic.
-The Knowledge Integration Service (KIS) imports the annotated standard names (e.g., CSDMS standard names \citep{peckham2014CSN}, the controlled vocabulary of observations data model \citep{horsburgh2009}, ingesting their thesaurus, and updates them into the GeoSemantics Wiki (a wiki describing the relationship between different standard names) and the triple store.
-The Knowledge Discovery Service (KDS) conducts semantic search and finds required resource in the triple store.
-The Semantic Annotation Service (SAS) annotates the metadata of resources in online repository (e.g., Clowder, an online resource collections developed under GeoSemantics framework).
-And the Resource Alignment Service (RAS) ensures the semantic consistency of information flowing between either serviced models (e.g., SEM) or a serviced model and serviced dataset (e.g.,  Clowder).
-In this study, we focus on the utilization of RAS on integration of SEMs to help envisioning the “Model Web”.
+Nevertheless, despite the advantage of the tight-coupling approach that the framework entirely controls both the data structures and processes of all parts of the model, it is difficult to couple models not following the standard or convention due to the fixed convention or standard of a framework.
+On the contrary, through the service-oriented loose-coupling approach, modelers only need to focus on the standardization of web interface and the protocol of data exchanging \citep{goodall2011}.
+As shown in \ref{tightLooseCouple}, by using web technology, the functionality of a model can be exposed as a web service with a specific protocol for data communication.
+In this case, by being conserved in its own hardward environment, any model requiring large data consumption or complicated configuration process can be easily coupled into any workflow or big decission system.
+It then also allows individual model developers or groups to maintain and update their models conveniently.
 
@@
 \centering
-\includegraphics[scale=0.3]{../figures/figure_2}
-\label{figure2}
-\caption{The architecture of GeoSemantic framework.
-Four web services (i.e., KIS, KDS, SAS and RAS) are developed to allow users to import or ingest the standard names into the triple store, discover the inherent relationships between the resources from the triple store, annotate metadata of resources semantically and align two heterogeneous resources.
-In this study, we focus on the application of RAS in coupling SEM to envision the Model Web.}
+\includegraphics[scale=0.25]{../figures/figure_tight_loose_couple.pdf}
+\label{tightLooseCouple}
+\caption{A comparison between the tight-coupling approach and the serviced-oriented loose-coupling approach: (a) all the models are linked under the same framework and operated in the same hard environment; (b) the models implemented under various hard environment talk with each other by exposing their functionalities through web services.
+}
 \end{figure}
 
-\section{Methodology}In this section, we present the architecture of how to ensure the semantic interoperability of serviced models as shown in Figure \ref{figure3}.
-To add a semantic layer on top of the available or new web serviced models, SEM is put forward by creating a dynamic metadata schema for processing these serviced models with minimum hum interventions.
-Then, RAS  is applied to ensure and do the required semantic alignment between the fields of the metadata schema of the relevant models in terms of (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) conversion of different file types; (4) temporal alignment of resources time horizon; (5) spatial alignment of resources spatial attributes.
+Therefore, MaaS or DaaS, being able to exchange data with other serviced models over the web, requires a uniform communication protocol for information exchanging.
+In geoscience, the applied protocols include Water Markup Language (WaterML) and the Open Geospatial Consortium (OGC) standards for transmitting hydrologic time series data and geospatial data, respectively.
+WaterML is initially applied as the protocol of hydrologic data transmission in WaterOneFlow web services held by Consortium of Universities for the Advancement of Hydrologic Scienc, Inc - Hydrologic Information System (CUAHSI-HIS, \cite{valentine2007}).
+Now the second version of WaterML is adopted as one of the OGC standards.
+Furthermore, various types of standards are published by the OGC, which includes but not limited to: (1) specifications for data format such as geography markup language (GML)and keyhole markup language (KML); (2) specifications for data publication such as web coverage service (WCS), web mapping service (WMS) and web feature service (WFS); and (3) specifiations for geoprocessing such as web processing service (WPS).\cite{swain2015} provides a good review of the current open source solutions for water resources web application, most of which apply various OGC standards.
+In this study, as a geoprocessing standard, OGC WPS is implemented by the web serviced model, which has proven to be successfully applied in other modeling studies requiring data exchanging between services \citep{castronova2013, goodall2011, schaeffer2008,vitolo2012}.
 
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.4]{../figures/figure_3}
-\label{figure3}
-\caption{The functionality of RAS in aligning the input and outputs of the serviced models.}
-\end{figure}
-
-\subsection{Semantically-Enabled Model(SEM)}The objective of SEM is to put a semantic layer on top of a serviced model to allow the external features of the model available and processable for other service like RAS.
-The models are exposed as services through the Open Geospatial Consortium (OGC) Web Processing Service (WPS).
-WPS is utilized because it provides a standard for processing data \citep{schut2007opengis}, which has proven to be successfully applied in other modeling study requiring data exchanging between services \citep{castronova2013, goodall2011, schaeffer2008,vitolo2012}.
-
-As depicted in the design of SEM in Figure \ref{figure4}, the semantic layer of SEM is added by creating a dynamic metadata schema based on a specified variable template in JSON format, which describes the name, the unit, the type, and the tempo-spatial properties of variable.
-The JSON-based metadata of a web serviced model includes not only the inputs and outputs but also the Uniform Resource Identifier (URI) for model execution.
-The metadata is assumed to live with the model codes in a same remote server and be serviced as well.
-It means the metadata of SEM is also available through an HTTP GET, with a different URI but the same namespace compared with the URI for the model execution through WPS.
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.4]{../figures/figure_4}
-\label{figure4}
-\caption{Design of Semantically-Enabled Model (SEM) with a variable template example for \textit{Rainfall}.}
-\end{figure}
-
-To completely contain information of a variable used in a model, the basic elements of the JSON-based variable template include:
-
-\paragraph{variableName} It illustrates the name of variable, with two keys: \textit{value} and \textit{type}.
-The field of type could be either “uri” or “string”, which indicates the field of \textit{value} as a URI or a simple string, respectively.
-
-\paragraph{unit} It illustrates the unit of variable, with two keys: \textit{value} and \textit{type} functioning same as those of \textit{variableName}.
-
-\paragraph{variableType} It illustrates the value, data and file type of variable in keys \textit{valueType}, \textit{storageType} and \textit{fileExtension}, respectively.
-The basic value types include integer, float, double, boolean, string and so forth.
-The field of storageType contains “singleValue” (a single value), “list” (a list of values) and “matrix” (a matrix of values).
-And the file type is detailed in \textit{fileExtension} (e.g., “.csv” for the Comma Separated Values (CSV) file, “.nc” for the Network Common Data Form (netCDF) file).
-Furthermore, to allow RAS be aware of where to store or pick up the data file, two other keys are added in \textit{variableType}: \textit{storagePath} and \textit{pickupPath}, with URIs as fields indicating the location of the file.
-Furthermore, \textit{storagePahHead} and \textit{pickupPathHead} indicate the headers of the data in the files with \textit{storagePath} and \textit{pickupPath}, respectively, if any.
-
-\paragraph{timeHorizon} It illustrates the temporal property of variable, with keys: \textit{start}, \textit{end} and \textit{step}.
-\textit{start} and \textit{end} are the start and end time of variable used in the model.
-Both of them have two keys: \textit{value} and \textit{format}, where format indicates the format or standard (e.g., ISO8601) of the field of \textit{value}.
-If the start and end times are not required by the model, the fields of value of \textit{start} and \textit{end} are entered as “notSpecified”.
-Moreover, \textit{step} describes the time step of variable, with information of time step value and time step unit (e.g., “h” for hour, “min” for minute) stored in keys \textit{value} and \textit{unit}.
-
-\paragraph{spatialProperty} It illustrates the spatial property of variable, with keys: \textit{boundaries}, \textit{LatStep}, \textit{LonStep} and \textit{gridType}.
-\textit{boundaries} contains the boundaries of variable, stored either in a bounding box (with key \textit{boundingBox}) or a shape file (with key \textit{shapeFile}).
-The latitude and longitude resolutions of variable are depicted in \textit{LatStep} and \textit{LonStep} with keys \textit{value} and \textit{unit}.
-Finally, the type of grid (e.g., uniform, rectilinear) is described in \textit{gridType}.
-
-It should be noted that if variable used in a model does not have any information for an attribute (key), the field of it is entered as “None”.
-For example, for a time series of rainfall at a specified location, the fields of all keys in \textit{spatialProperty} should be escaped as “None”.
-
-\subsection{Resource Alignment Service (RAS)} RAS is developed as a service to ensure the semantic consistency of information exchanging between online resources.
-The entire functionality of it includes semantic mediation of variable names, conversion of mismatched units and file type, and tempo-spatial alignment.
-A Python web application package, Flask\footnote{http://flask.pocoo.org/}, is utilized to set up the service.
-In this study, it is applied to align quantities flowing between SEM.
-
-\subsubsection{RAS Architecture}As shown in Figure \ref{figure5}, RAS is a web service allowing the alignment between two list variables in terms of: variable name, variable unit, variable value type, file type, variable temporal and spatial properties.
-The alignment is carried out for each pair of variables, say, aligning from variable I to variable II.
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.4]{../figures/figure_5}
-\label{figure5}
-\caption{The architecture of the Resource Alignment Service (RAS).}
-\end{figure}
-
-\paragraph{variable name} The semantic mediation of two variable names is conducted through either a SKOS-based search or a string-based search.
-SKOS-based search is applied for variable names in a form of URI.
-The procedures of it are (1) finding all the matched (i.e., \textit{skos:exactMatch} or \textit{skos:closeMatch}) variable names for variable I by querying the standard names graph through SPARQL\footnote{http://www.w3.org/TR/rdf-sparql-query/}, an Resource Description Framework (RDF) query language; (2) checking whether variable II is in the list of the matched variables of variable I (return matched if true).
-\textit{rdflib}\footnote{https://github.com/RDFLib/rdflib}, a Python library for working with RDF, is utilized for RDF querying.
-In addition, if the types of variable names are string, then the mediation is through string-based search.
-The variable name in string is first transformed in a URI format by assigning it with a model name space.
-Then SKOS-based search is used for semantic mediation.
-
-\paragraph{variable unit} Similar to the alignment of two variable names, the conversion of two variable units is based on \textit{natu} conversion and SWEET unit conversion, according to the types of units: string and URI, respectively.
-If the unit types are string, a Python unit conversion package, \textit{natu}\footnote{http://kdavies4.github.io/natu/} (Natural units in Python), is employed to perform the conversion.
-On the other hand, SWEET unit ontology is applied in the case that both the unit formats are URI.
-
-\paragraph{variable type} The alignment of the variable types of two variables is based on both the value and file types conversion.
-The value type alignment is straightforward through type conversion in Python (e.g., from \textit{float} to \textit{integer}).
-In terms of conversion in file types, currently the supported file types are csv/txt, xls and.nc, with the header information in the file if any.
-
-\paragraph{variable time horizon} The temporal property alignment of two variables is conducted through linear temporal interpolation, given the start time, the end time and the time step of each variable.
-By temporal interpolation approach, the actual time period of the data of variable II aligned from that of variable I is the intersection of the given time periods of the two variables.
-It means if the time periods (from the start time to the end time) of the two variables do not overlap, there is no data interpolated for variable II.
-
-\paragraph{variable spatial property} The alignment of two variables’ spatial property is carried out through regridding and projection.
-Based on the boundary and grid information of two variables, regridding is utilized for spatial interpolation from grids of variable I to those of variable II.
-Also, projection, or map projection is a transformation from the latitudes and longitudes of locations on earth of a sphere into grids or locations in a plane.
-This functionality is still under development.
-
-\subsubsection{RAS Functionality} The purpose of RAS is to avoid the semantic mismatch of two variable lists by aligning each pair of variables through the functions described in Section 2.2.1.
-Generally, through HTTP POST method, the service takes the metadata of the two variables lists, along with the values of a list of variables, in JSON format.
-For example, to apply RAS to ensure that the output(s) of a SEM (say, SEM I) can be utilized as the input(s) of another SEM (say, SEM II), the following information is required to be fed into RAS:
-\begin{itemize}
-\item the metadata of the output(s) of SEM I
-\item the output values of SEM I
-\item the metadata of the input(s) of SEM II
-\end{itemize}
-Then, the process of the semantic check and the alignment happens inside of the RAS service based on the alignment functions for the different properties (i.e., name, unit, type, time horizon and spatial property).
-In the case of alignment between input and output of two SEMs, the process is conducted based on the metadata of the two SEMs, which is introduced in Section 3.1.
-Once the alignment process finishes, the values of the other variable list, aligned from the provided values of the first list, is returned 262 in JSON format.
-
-In addition, it should be noted that for each pair of variables, the alignment would fail in the cases of the following situations:
-\begin{itemize}
-\item the two variable names are mismatched through either SKOS-based or string-based search
-\item the storage types of the two variables are not the same (e.g., one is a single value, another is a list of values).
-\end{itemize}
-
-\section{Application} Two applications are presented: (1) serviced data-model integration (DaaS $\rightarrow$ MaaS) and (2) serviced model-model integration (DaaS $\rightarrow$ MaaS $\rightarrow$ MaaS).
-All the MaaS are deployed as SEMs and RAS is utilized for ensuring the semantic interoperability between serviced resources.
-In the first application, DaaS $\rightarrow$ MaaS, meteorological data stored Clowder is aligned to the format of the inputs of a SEM-based Priest-Taylor model through RAS.
-In the application of DaaS $\rightarrow$ MaaS $\rightarrow$ MaaS, RAS is used for the alignment between both the data from Clowder and the output of Priest-Taylor model and a SEM-based 1D Richard equation model.
-
-\subsection{DaaS and MaaS in Application} 
-\subsubsection{SEMs in Application} The Priestley-Taylor approach is an approach for estimating evaporation at areas with low moisture stress, a modification of Penman’ approach for evaporation estimation \citep{priestley1972}.
-It requires information of net short wave and long wave radiation, ground heat flux and air temperature at a specific location.
-In this study, the ground heat flux is generated from a linear relationship between it and soil temperatures at different levels.
-
-Richards’ equation, developed by \cite{richards1931}, simulates the water movement process in unsaturated soils.
-Given the time series information of evaporation and precipitation, Richard’s equation is able to generate the profiles of both the soil pressure head and the soil moisture over time by solving its non-linear partial differential equation.
-In this study, 1D Richards equation is utilized in the application, which simplifies the whole process by considering the vertical direction.
-
-Both the models are serviced through PyWPS\footnote{http://pywps.wald.intevation.org/}, a Python implementation of WPS.
-The original codes of the two models are in Python and MATLAB for Priest-Taylor and 1D Richard equation, respectively.
-To allow the MATLAB-based 1D Richard equation model serviced by PyWPS, the package, MATLAB Engine for Python \footnote{http://www.mathworks.com/help/matlab/matlab-engine-for-python.html}, is used to enable calling MATLAB code from Python.
-Also, the JSON-based metadata of the two models, of which the example is provided in Figure \ref{figure4}, are also serviced and available through HTTP GET request, which is set up by Flask.
-
-\subsubsection{Clowder} In addition, Clowder, as a product of GeoSemantic framework, is developed as an online resource (i.e., model and data) repository allowing resource upload, annotation and extraction of the metadata of the resource.
-Users can annotate or extract the metadata of a resource through either a web page interface or web service APIs.
-The metadata available for annotation includes temporal/spatial reference, description, variable name mapping, abstract and so forth.
-To feed the required inputs of the two models, the soil surface temperature, the net short and long wave radiation, the air temperature, the precipitation and the soil temperature at depth of 4 meter in 2007 at Bondville are uploaded and annotated in Clowderas 306 shown in Figure \ref{figure6}.
-
-\begin{landscape}
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.4]{../figures/figure_6}
-\label{figure6}
-\caption{The screenshots of the five environmental datasets at Bondville in 2007 uploaded to Clowder and the metadata of \textit{precipitation.csv} file.}
-\end{figure}
-\end{landscape}
-
-\subsubsection{Relations and Heterogeneities among Data in Clowder and Variables in the two SEMs} Figure \ref{figure7} illustrates the relationships among the data stored in Clowder and the I/O of the two SEMs.
-In the first application (i.e., DaaS $\rightarrow$ MaaS), information stored in Clowder (i.e., the surface temperature, net long and short wave radiation, air temperature and soil temperature at depth of 4 meters at Bondville in 2007) is used for the input of the serviced Priest-Taylor model after a certain alignment through RAS.
-For the second application, the required inputs of 1D Richard equation are given by both the precipitation at Bondville in 2007 from Clowder and the evaporation output of the Priestley-Taylor model generated from the first application.
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.4]{../figures/figure_7}
-\label{figure7}
-\caption{The relationships among the Bonville’s environmental data in 2007 from Clowder and the inputs and outputs of Priestley-Taylor model and 1D Richard equation.}
-\end{figure}
-
-In both applications, RAS is utilized to ensure the semantic consistency of quantities flowing from either Clowder or the SEM’s output to the inputs of the twoSEMs.
-The semantic heterogeneities of the data used in Clowderand the I/O of the two models are provided in Table \ref{tabel1}.
-It can be observed that the variables or data differ from each other in terms of name, unit, value type, file extension and time horizon properties.
-In terms of naming, the names of data from Clowder are defined with an underscore separating words while variable names in the two models are in format of camelCase.
-Units and file extension of variables are also different.
-For example, the unit of data “precipitation” in Clowder is in mm while the required unit of the input “Rainfall” in 1D Richard equation is in cm; the format of Priestley-Taylor model’s output (“LandSurfaceEvaporation”) is netCDF but the “Evaporation” of 1D Richard equation requires CSV file.
-For time horizon, we assume that both the Priestley-Taylor model and 1D Richard equation has the same fixed time range but with different time steps as 1h and 0.5h, respectively.
-The fixed time range of the two models is for differing from the period of time of data from Clowder which covers the whole year 2007.
-
-\begin{landscape}
-\begin{table}[h]
-\small
-\centering
-\renewcommand{\arraystretch}{0.6}
-\caption{The properties of the Clowder's data used in this study.}
-\label{tabel1}
-\begin{tabular}{*8c}
-\toprule
-Clowder&Name&Unit &Value type&File extension & Start time & End time & Time step                      \\
-\midrule
-\multirow{6}{*}{Data}&air\_temperature                      & degF        & double    & .csv  & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
-					    	      &surface\_temperature               & degF       & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
-							  &soil\_temp\_4m\_underground & degF        & double    & .csv  & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
-							  &net\_longwave\_radiation         & W*m-2     & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
-							  &net\_shortwave\_radiation       & W*m-2      & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h       \\
-							  &precipitation                             & mm           & double    & .csv   & 2007-01-01T00:00:00Z & 2007-12-31T23:59:59Z & 12h      \\
-\midrule
-Priestley-Taylor model&Name&Unit &Value type&File extension & Start time & End time & Time step                      \\
-\midrule
-\multirow{6}{*}{Input}&AirTemperature                     & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &NetLongwaveRadiation        & W*m-2   & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &NetShortwaveRadiation        & W*m-2  & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &SoilTempAtSurface               & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &SoilTempAtDepthOfXMeters & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &SoilDepthOfXMeters	           & m           & double    & /        & /								  & /								    & /      \\
-Output                      &LandSurfaceEvaporation       & m           & double    & .nc     & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-\midrule
-1D Richard equation&Name&Unit &Value type&File extension & Start time & End time & Time step                      \\
-\midrule
-\multirow{6}{*}{Input}&AirTemperature                     & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &NetLongwaveRadiation        & W*m-2   & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &NetShortwaveRadiation        & W*m-2  & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &SoilTempAtSurface               & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &SoilTempAtDepthOfXMeters & degC     & double    & .csv   & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-							  &SoilDepthOfXMeters	           & m           & double    & /        & /								  & /								    & /      \\
-Output                      &LandSurfaceEvaporation       & m           & double    & .nc     & 2007-05-01T00:00:00Z & 2007-08-31T23:59:59Z & 1h       \\
-\bottomrule
-\end{tabular}
-\end{table}
-\end{landscape}
-
-\subsection{Implementation} A workflow is created to carry out the coupling of heterogeneous data and models as presented in Figure \ref{figure7}.
-Basically, in the first application, based on the metadata of Priestley-Taylor model, data of \textit{air\_temperature}, \textit{surface\_temperature}, \textit{soil\_temperature\_underground}, \textit{net\_longwave\_radiation}  and \textit{net\_shortwave\_radiation} in Clowder is first aligned to the required semantics of the inputs of the Priestley-Taylor model by RAS.
-Then, once the input is ready, the model execution is conducted through a HTTP request to the WPS-based service.
-In the second application, RAS is used again to align from the output of Priestley-Taylor model and \textit{precipitation} data in Clowder to the two inputs of 1D Richard equation.
-The Richard equation execution is performed after the alignment.
-
-To ensure the successful alignment through RAS, besides the utilization of the several conversion functions (e.g., unit conversion, temporal interpolation), a comprehensive standard names graph is also required for the semantic mediation of variable names.
-Figure \ref{figure8} shows how the variable names in Table \ref{tabel1} are related with each other by using SKOS.
-For example, \textit{AirTemperature} in Priestley-Taylor model is matched with \textit{air\_temperature} in Clowder based on their same \textit{skos:exactMatch} \textit{csn:atmosphere\_bottom\_air\_\_temperature}, a CSDMS standard name for describing air temperature at the bottom of the atmosphere.
-
-\begin{landscape}
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.3]{../figures/figure_8}
-\label{figure8}
-\caption{The SKOS-based relationships between CSDMS standard names and the variable names in the application stored in the standard names graph.}
-\end{figure}
-\end{landscape}
-
-\section{Summary and Future Work} An approach for ensuring the semantic consistency of information exchanging between serviced resources was designed to help integrating serviced models.
-To solve the semantic interoperability issue in envisioning a world of Model Web, serviced models or MaaS were semantically enabled as SEM with the application of the Resource Alignment Service (RAS) in dealing with the semantic inconsistency of quantities exchanging between SEMs.
-To allow the external features (e.g., inputs and outputs) of a model available for other clients (e.g., users or services), Semantically-Enabled Models (SEM) were put forward by adding semantic layer on top of a serviced model and the Open Geospatial Consortium’s (OGC) Web Processing Service (WPS) standard was utilized as the data specification.
-Based on the semantic information of SEM, RAS was then applied to check and resolve the misalignment of two lists of variables in terms of names, units, value and file types, temporal and spatial properties.
-
-A workflow of heterogeneous collection of serviced data and SEMs was created to show how RAS can seamlessly align the semantics of quantities exchanged between these resources.
-Priestley-Taylor model and 1D Richard equation were deployed as SEM serviced by PyWPS.
-Environmental data stored in Clowder was fed as inputs for the two models to create the workflow in a manner of DaaS $\rightarrow$ MaaS $\rightarrow$ MaaS as shown in Figure \ref{figure7}.
-The heterogeneities of data in Clowder and variables in the two models are presented in Table \ref{tabel1}.
-With the implementation shown in Section 4.2, we conclude that it is possible to resolve the semantic interoperability issue of coupling web serviced models by enhancing the semantic information for the model and using an alignment tool such as RAS to achieve reduce the semantic consistency.
-
-Nevertheless, as RAS is still under development, the functionality of RAS can be enhanced in the following points.
-First, the functions for spatial alignment are required, which probably includes the regridding (an interpolation process from one grid to another grid) and projection (a transformation process from one coordinate system to another coordinate system).
-The OGC standards could provide a good option to record the spatial information of a variable used in a specific model with a specific tools conducting the spatial alignment, like ESMF Python Regridding Interface \footnote{https://www.earthsystemcog.org/projects/esmpy/}.
-Additionally, a more comprehensive file type conversion tool is required.
-Current file type conversion utility in RAS only supports CSV, Excel and netCDF files, with emphasis on tabular file format.
-Software like Polyglot \footnote{http://opensource.ncsa.illinois.edu/projects/POL}, a distributed service capable of file format conversions, might be a choice for conversion of more file types.
-Moreover, for structured file formats (e.g., netCDF, Gridded Binary (GRIB)), a simple header information is not enough for describing the required data content in the file despite of its current usage in the variable template for SEM.
-Therefore, instead of a specified header, an extra document describing the internal information of the data file could be better in providing the semantic information of the data in the file.
-For example, netCDF-LD, ''a convention for encoding netCDF based on Linked Data principles'' \citep{yu2015}, might be applied for enhancing the semantics of a netCDF file.
-
-Finally, we here only try to solve the issue of the semantic interoperability in coupling serviced models.
-To envision the world of Model Web, more works are required to tackle the other technical challenges, as summarized by \cite{nativi2013}.
-One of them is the high performance challenges.
-The primary disadvantage of loosely-coupled, service-oriented modeling is that it might affect computation efficiency negatively when large datasets are required to transfer via the internet for the initialization or parameterization of the serviced models \cite{goodall2011}.
-Another challenge is related to the reliability or long term access of the services.
-The service might be unavailable for the users due to different reasons (e.g., the broken or updates of the remote server), thus disabling all the clients utilizing it.
-Issues described above need further investigations
-
-\section*{Acknowledgement} The authors wish to acknowledge the auspice of NSF Grant Council (project numbers ICER 1440315, ACI 12-61582, ACI 0940824, and EAR-1331906) for the support of this study.
-The gratitude is also extended to Luigi Marini and Rui Liu from NCSA at the University of Illinois at Urbana-Champaign for their help and comments in deploying the service.
+The OGC WPS provides an approach for standardizing data processing, including three methods: GetCapabilities, DescribeProcess and Execute.
+The GetCapabilities method allows clients to receive a list of existing processes or models from the remote server implementing the WPS.
+The DescribeProcess method replies clients with the metadata of the inputs and outputs of a specific model or process.
+Finally, the execution of a model or process can be conducted through the Execute method based on the input values from clients.
+All the three methods can be requested by either HTTP POST or HTTP GET method.
+In this study, models are implemented by WPS, and we utilized the DescribeProcess and Execute method for retrieving the metadata specifics of the models and the model execution, respectively.
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2015-07-17 texfiles/manuscript.tex
- Revise the Introduction and Design Requirement and Overview. - Create the general comment folder to include all the comments from both Mostafa and Praveen

@@
 
-\title{Towards Decentralized Integration of Environmental Resources on the Web: A Resource Alignment Service}
+\title{Towards Decentralized Integration of Environmental Models on the Web: A Resource Alignment Service}
 
@@
 \author[address1]{Mostafa Elag}
-\author[address2]{Luigi Marini}
-\author[address2]{Liu Rui}
 \author[address1]{Praveen Kumar\corref{correspondingauthor}}
-
 \cortext[correspondingauthor]{Corresponding author}
 \ead{kumar1@illinois.edu}
+\author[address2]{Liu Rui}
+\author[address2]{Luigi Marini}
 
@@
 
-\section{Introduction}For decades, integrated environmental modeling has been applied in investigating the mechanism of the entire ecosystem, which becomes increasingly complex under climate change and human impact recently \citep{argent2004, laniak2013}.
-With the growing efforts in integrated modeling, scientists with a solo discipline background are able to access, reuse and couple reosurces (i.e.,  models and data) from various disciplines.
-It therefore enhances their assessment, prediction and management abilities of a complicated natural system.
-One of the approaches is through envisioning a world of ''Model Web'', where the functionalities of a model are exposed through web services and then integrated via the internet \citep{geller2007, geller2008, nativi2013}.
-As stated by \cite{nativi2013}, one of the challenges in achieving the web-serviced model integration is to ensure the 'minimal barriers to entry' or the interpoerability between the serviced resources.
-In this study, we aim to envision a world of 'Model Web' with emphasis on ensuring the semantic consistency of information flowing between web-serviced resources in geoscience.
+\section{Introduction}Integrated environmental modeling is essential in simulating a complex ecosystem \citep{argent2004}.
+This is because individual scientists or small research groups usually have different practise in modeling in terms of programming language, variable names, units and other factors, causing models from various disciplines hard to be accessed, reused and coupled.
+Thanks to the advance of web technology, models are able to be exposed as web services (or called as Model as a Service (MaaS)), and integrating these web serviced models over web thus becomes promising \citep{goodall2011}.
+The traditional integrated modeling approach often requires models to be encapsulated in a specific framework or standard.
+Meanwhile, coupling models over the web provides an opportunity that models can be independent of any framework or standard by only exposing their functionalities as web services.
+In this study, we aim to integrate web serviced models in geoscience by utilizing a Resource Alignment Service (RAS), which is able to ensure the semantic consistency of information flowing between web-serviced resources (i.e., model and data).
 
-The application of service-oriented architecture in environmental modeling just starts recently \citep{castronova2013, mineter2003, granell2010, goodall2011, goodall2013}.
-Folliwng the concept of Software as a Service (SaaS), models and data can also be exposed as web services, called as Model as a Serice (MaaS) and Data as a Service (DaaS), respectively.
-To achieve a world of interoperable MaaS and DaaS, the concept of ''Model Web'' was put forward by \citep{geller2008}.
-Later, \cite{nativi2013} explicitly defined it as ''a dynamic web of models, integrated with databases and websites, to form a consultative infrastructure where researches, managers, policy makers, and the general public can go to gain insight into ‘what if’ questions'' in initiating it under the project of the Group on Earth Observation.
-Several efforts have been made to draw the picture of “Model Web”.
-\citet{goodall2011} exposed water resource models as web services through the Open Geospatial Consortium (OGC) Web Processing Service (WPS) and demonstrated how it could be encapsulated as OpenMI(open modeling interface and environment)-compliant models.
-Then, they furthered the idea of servicing an OpenMI-compliant model based on WPS by considering the case of time-dependent models \citep{castronova2013}.
-Furthermore, an OpenMI-ESMF web service wrapper was developed to couple a climate model implemented via ESMF web service with an OpenMI-compliant hydrologic model running on a personal computer \citep{goodall2013}.
+Traditionally, scientists usually apply a specific framework or standard for coupling their research-required models to tackle the heterogeneity issue of models.
+To name a few, Community Surface Dynamics Modeling System (CSDMS) \citep{peckham2013}, OpenMI standard \citep{moore2005} and Earth System Modeling Framework \citep{hill2004}.
+Such tight coupling approach controls both the data structures and processes of all parts of the model.
+For example, in CSDMS community, each model is wrapped by a BMI (Basic Model Interface) wrapper and coupled with other models under a common framework, as shown in Figure 1(a).
+The OpenMI provdies a standard\footnote{http://www.opengeospatial.org/node/1822} to convert standalone models into OpenMI-compliant models, and then couples them by using a set of utilities (see Figure 1(b)).
+Despite of the succesful applications of the tight coupling approach, a factor that cannot be ignored is the difficulty of coupling models that do not follow the same standards or frameworks.
+There is a need, therefore, to decentralize model integration.
 
-One of the key challenges in model integration communinity is the heterogeneity or long-tail property of models and data.
-Due to different habits of research groups or individual scientists, models developed by them would probably differ in operating system, programming language, variable name, data unit, temporal-spatial property and so forth.
-In the world of Model Web, a user of a web-serviced model does not need to consider the operating system or programming language of which the model is serviced and implemented because he or she only interacts with the exposed service.
-But the user is required to be aware of both the communication protocol the service applies and the remaining heterogeneities (e.g., variable name, data units).
-Otherwise, the semantic inconsistency of information flowing between services would impact the functionaility of a web serivce negatively as shown in \ref{semanticInconsistency}.
-To achieve a seamless integration of serviced resources, a uniform protocol and an aligning mechanism are required for information processing and ensuring reducing the semantic consistency of data flowing between serviced resources, respectively.
-The existing efforts described in the previous paragraph try to achieve such interoperability by applying a specific standard.
-For instance, apply OpenMI standard in integrating water resource models serviced by WPS \citep{goodall2011, castronova2013}.
-Nevertheless, the application of a certain standard or framework might not be fruitful.
-This is because the existence of different frameworks in different domains might imply the adoption of a specific framework in one discipline, thus complicating the online communication of serviced resources from various disciplines.
-For example, an OpenMI-compliant serviced model cannot talk with a serviced model embedded in Object Modeling System (OMS, \cite{david2013}) without a proper wrapper for communication between OpenMI and OMS.
-Furthermore, standards like OpenMI do not allow semantic mediation between variable names, prohibiting the integration of models with variables in alias names.
+The service-oriented, loose-coupling approach gives the potential to integrate models independent of any framework over the web.
+Being exposed as web services, models can be conserved in their own hardware environments.
+As shown in Figure 1(c), the decentralized integration of web serviced models is independent of any integration framework and operating system.
+Thus, modelers only need to focus on the standardization of the web interface and the protocol of data exchanging \citep{goodall2013}.
+Web serviced models can ''talk'' to each other if the semantic consistency of quantities exchanged between them is ensured by a utility or web service (e.g., the Resource Alignment Service used in this study).
 
@@
 \centering
-\includegraphics[scale=0.4]{../figures/figure_MaaS_misalignment.pdf}
-\label{semanticInconsistency}
-\caption{An illustration of the semantic inconsistency between two web serviced models.}
+\includegraphics[scale=0.5]{../figures/comparison.pdf}
+\caption{A comparison of the traditional tight integration centralized in a specific framework and the decentralized integration through web services.
+(a) the model integration in CSDMS framework operated in a Unix machine; (b) the integration of OpenMI-compliant models operated in a Windows machine; (c) the decentralized integration of web serviced models operated in various operating system.}
+\label{comparison}
 \end{figure}
 
-To tackle the issue of semantic interoperability of integrating service-oriented modeling, we develop a web service named Resource Alignment Service (RAS) to ensure semantic consistency of information exchanged between MaaS over the web, including: (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) temporal alignment of resource time horizon and (4) spatial alignment of resources spatial attributes.
-Models are implemented by the WPS, which exposes both its execution and its inputs and outputs (I/O) properties through web service.
-Then, RAS is utilized to align the quantities exchanging between MaaS over the webthe two types of serviced models.
+Until recently, the application of the service-oriented architecture in environmental modeling starts \citep{castronova2013, mineter2003, granell2010, goodall2011, goodall2013}.
+Following the concept of Software as a Service (SaaS), models and data can also be exposed as web services, called as Model as a Service (MaaS) and Data as a Service (DaaS) respectively.
+\cite{goodall2011} exposed water resource models as web services by using the Open Geospatial Consortium (OGC) Web Processing Service (WPS) and demonstrated how it could be encapsulated as OpenMI-compliant models.
+Then, \cite{castronova2013} furthered the idea of servicing an OpenMI-compliant model based on WPS by considering the case of time-dependent models.
+In addition, an OpenMI-ESMF web service wrapper was developed to couple a climate model implemented via ESMF web service with an OpenMI-compliant hydrologic model running on a personal computer \citep{goodall2013}.
+Furthermore, the concept of ''Model Web'' was put forward to draw the picture of a world of interoperable MaaS and DaaS \citep{geller2007, geller2008}.
+\cite{nativi2013} then adopted the idea of ''Model Web'' in the Group on Earth Observation (GEO) Model Web initiative.
+Nevertheless, none of the existing efforts in coupling serviced models, either the application of OpenMI standard in integrating web serviced models or the proposed concept of ''Model Web'', has solved the semantic interoperability issue entirely independent of a modeling integration framework.
 
-In the remainder of the paper, Section 2 describes the design requirement and provides a short overview on model integration community.
-In Section 3, the architecture of the Resource Alignment Service (RAS is presented, including the an brief overview of GeoSemantic framework, the functionality and the components of RAS.
+Therefore, in this paper, we develop a web service named Resource Alignment Service (RAS) to ensure semantic consistency of information exchanged between the decentralized web serviced models over the web.
+The capability of RAS includes (1) semantic mediation between variable names; (2) conversion of mismatched units; (3) temporal alignment of resource time horizon and (4) spatial alignment of resources spatial attributes.
+Models are implemented by the WPS, which provides an interface standard for exposing both the model execution and the obtain of a model's input(s) and output(s) as web services.
+Then, RAS is utilized to align the quantities exchanged between the WPS-implemented serviced models.
+
+In the remainder of the paper, Section 2 describes the design requirement of the decentralized integration of web serviced models.
+In Section 3, the architecture of the Resource Alignment Service (RAS) is presented, including the an brief overview of GeoSemantic framework, the functionality and the components of RAS.
 Section 4 demonstrates the application of RAS in coupling WPS-implemented models with the input data from Clowder, an online data repository.
@@
 
-\section{Design Requirement and Overview}
-Modeling integration in geoscience has advanced significantly these years because of the increasing collaboration between scientists or research groups from various disciplines (e.g., hydrology, geology, ecology and so on).
-The traditional integrated modeling approach is through tight coupling, where the initial independent models are coupled under a modeling integration application or framework.
-The representative integration frameworks include the Community Surface Dynamics Modeling System (CSDMS), Earth System Modeling Framework (ESMF), OpenMI standard and so forth \citep{hill2004, peckham2013, moore2005}.
-The CSDMS architecture employs the component-based modeling approach, where standand-alone models are encapsulated and coulped with others in a plug-and-play manner.
-For each model, a BMI (Basic Model Interface) file is required for recording the model's basic information and converting it into a plug-and-play component.
-Then, the integration process is conducted in the Component Model Interface based on all the utilities provided by CSDMS frameowork.
-ESMF is aimed at coupling models from Earth science (e.g., wearther and climate model), with a 'sandwich' pattern characterizing its architecture \citep{hill2004}.
-The user code layer contains all the model components in ESMF, which are then encapsulated in the superstructure layer aligning and connecting the input and output data between models.
-All the utilities for the alignment are provided in the infrastructure layer.
-In addition, OpenMI is an effort on model coupling in water resource community.
-It provides a standard interface for any new or existing models exchanging data with each other during running period.
-Now the OpenMI standard is adopted as a specification in the OGC.
+\section{Design Requirement and Overview} A service-oriented architecture is adopted for the decentralized integration of web serviced models.
+Hence, it is crucial to standardize the communication protocols of web services.
+In this paper, the OGC Web Processing Service (WPS) specification is implemented for setting up the interface of the serviced models.
 
-Nevertheless, despite the advantage of the tight-coupling approach that the framework entirely controls both the data structures and processes of all parts of the model, it is difficult to couple models not following the standard or convention due to the fixed convention or standard of a framework.
-On the contrary, through the service-oriented loose-coupling approach, modelers only need to focus on the standardization of web interface and the protocol of data exchanging \citep{goodall2011}.
-As shown in \ref{tightLooseCouple}, by using web technology, the functionality of a model can be exposed as a web service with a specific protocol for data communication.
-In this case, by being conserved in its own hardward environment, any model requiring large data consumption or complicated configuration process can be easily coupled into any workflow or big decission system.
-It then also allows individual model developers or groups to maintain and update their models conveniently.
+\subsection{Background} Service-oriented computing is the application of service-oriented architecture in computation, where models or computing components are distributed on various remote server and provide services to other clients via a communication protocol \citep{huhns2005, erl2004}.
+The client can be either a user or other web service consuming the functionality exposed over the internet.
+The service-oriented computing approach implies a loose coupling manner.
+Following a specific communication protocol, the client makes a request to the web service operating on a remote server over the web.
+Then, after receiving the request, the service interpretes the incoming information, carries out a certain processing and sends a response back to the client for further application.
+Based on such architecture, the web serviced models can be conserved in any hardware environment (e.g., operating system) and set up in any programming language.
+It is also convenient for modelers to maintain and update their models at the backend, without the entire web-based architecture being disturbed.
+Only the compliance of using a common web service standard and commnication protocol is required for the commnication between client and service successfully.
 
-\begin{figure}[!htbp]
-\centering
-\includegraphics[scale=0.25]{../figures/figure_tight_loose_couple.pdf}
-\label{tightLooseCouple}
-\caption{A comparison between the tight-coupling approach and the serviced-oriented loose-coupling approach: (a) all the models are linked under the same framework and operated in the same hard environment; (b) the models implemented under various hard environment talk with each other by exposing their functionalities through web services.
-}
-\end{figure}
+Written in a certain language (e.g., eXtensive Markup Language (XML) or JavaScript Object Notation (JSON)), the request data needs to follow a specific web service standard.
+Two common web service standards are the REpresentational State Transfer (REST) specifications and the Simple Object Access Protocol (SOAP).
+SOAP has been widely applied for setting up web service, usually combined with the Web Service Description Language (WSDL).
+However, a web service in SOAP/WSDL format is much more complex than a RESTful web service application \citep{mulligan2009}.
+This is because SOAP is designed for strutured information and therefore requires the incoming data to follow a certain prototype.
+Meanwhile, a RESTful application only relies on a stateless communication protocol (e.g., the Hypertext Transfer Protocol (HTTP)).
+By using a set of HTTP methods (GET, POST, PUT, DELETE, HEAD, \cite{fielding1999}), a RESTful application is able to interact with the resources exposed by a web service.
+In this study, we apply the RESTful application to design our servce-oriented computing for its simplicity and easy-to-use.
+Nevertheless, due to their general service application, neither SOAP or REST is designed for a specific application (e.g., geoscience).
+It is also necessary, therefore, to apply a web service standard following REST that is able to define how data is transfered over the web.
 
-Therefore, MaaS or DaaS, being able to exchange data with other serviced models over the web, requires a uniform communication protocol for information exchanging.
-In geoscience, the applied protocols include Water Markup Language (WaterML) and the Open Geospatial Consortium (OGC) standards for transmitting hydrologic time series data and geospatial data, respectively.
+In geoscience, much work has been done for the standardization of data transfered between web service.
+For example, Water Markup Language (WaterML) and the Open Geospatial Consortium (OGC) standards are used for transmitting hydrologic time series data and geospatial data respectively.
 WaterML is initially applied as the protocol of hydrologic data transmission in WaterOneFlow web services held by Consortium of Universities for the Advancement of Hydrologic Scienc, Inc - Hydrologic Information System (CUAHSI-HIS, \cite{valentine2007}).
@@
 
-The OGC WPS provides an approach for standardizing data processing, including three methods: GetCapabilities, DescribeProcess and Execute.
+\subsection{Serving models using the OGC WPS specification} The OGC WPS provides an approach for standardizing data processing, including three methods: GetCapabilities, DescribeProcess and Execute.
 The GetCapabilities method allows clients to receive a list of existing processes or models from the remote server implementing the WPS.
@@
 All the three methods can be requested by either HTTP POST or HTTP GET method.
-In this study, models are implemented by WPS, and we utilized the DescribeProcess and Execute method for retrieving the metadata specifics of the models and the model execution, respectively.
+In this study, models are implemented by WPS, and we utilized the DescribeProcess and Execute method for retrieving the metadata specifics of the models and the model execution respectively.
+
+PyWPS\footnote{http://pywps.wald.intevation.org/}, a Pythoon package for implementing WPS, is utilized for servicing models.
+The advantage is that PyWPS provides a module for modeler to apply WPS standard directly on any model.
+Set up on a specific web server (e.g., Apache\footnote{http://httpd.apache.org/} and Nginx\footnote{http://nginx.org/}), PyWPS is able to expose models as web services applying WPS specification.
 

### 2015-07-19 texfiles/manuscript.tex
some little revisions on figure 1 and keywords.
- Add another section "RAS Architecutre" by revising and combining the previous two sections"GeoSemantic" and "RAS"

@@
 \begin{keyword}
-Model Web \sep semantic interoperability \sep the Resource Alignment Service (RAS) 
+decentralized integration \sep web service \sep semantic interoperability \sep the Resource Alignment Service (RAS) 
 \end{keyword}
@@
 
+\section{RAS Architecture}The Resource Alignment Service (RAS) is a product of GeoSemantic framework \citep{elag2015}, a project aiming to resolve the semantic interoperability issue of various resources based on semantic web technology \citep{berners2001}.
+In this section, we first briefly introduce the GeoSemantic framework and how the RAS works under this framework.
+Then, the workflow of the RAS is presented, including the trigger (or the request inputs), utilizing information from GeoSemantic framework, passing information through its inherent aligning functions and returning back the alignment result.
+The components of the RAS are detailed at last.
+
+\subsection{GeoSemantic Framework}GeoSemantic framework is an ongoing project whose goal is to allow the structured information seamlessly exchanging between various resources by achieving their semantic interoperability \citep{elag2015}.
+Through semantic web technology, GeoSemantic enhances the capability of finding resources by searching a standard names grpah, discovering the implicit relationships between resources by reasoning, and annotating a new or an existing resource by adding semantic tags.
+A general architecture of it is presented in Figure \ref{geosemantic}, with emphasis on RAS's functionality.
+
+As emphasized in Figure \ref{geosemantic}, RAS ensures the semantic consistency of information flowing between various web serviced resources.
+For example, align data stored in Clowder\footnote{https://clowder.ncsa.illinois.edu/clowder/} (an online resource collections developed under GeoSemantic framework) to the inputs of a web serviced model.
+In this study, we focus on the utilization of RAS in coupling the WPS-implemented models to help decentralized integration of web serviced models.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[scale=0.5]{../figures/geosemantic.pdf}
+\caption{The architecture of GeoSemantic framework.
+Four web services are developed to allow users to import or ingest the standard names into the triple store, discover the inherent relationships between the resources from the triple store, annotate metadata of resources semantically and align two heterogeneous resources.}
+\label{geosemantic}
+\end{figure}
+
+\subsection{RAS Workflow}RAS is developed as a service being used for ensuring the semantic consistency of information exchanging between online resources.
+The entire functionality of it includes semantic mediation of variable names, conversion of mismatched units and file type, and tempo-spatial alignment.
+A Python web application package, Flask\footnote{http://flask.pocoo.org/}, is utilized to set up the service for RAS.
+
+A basic workflow of RAS is presented in Figure \ref{rasWorkflow}.
+Through HTTP POST method, RAS takes the metadata of two lists of variables, the formats of the two lists, and the values of the variable list to be aligned as posted data.
+The response of RAS is also in JSON format with two fields: \textit{aligned} and \textit{unaligned}.
+\textit{aligned} field includes all the variables being aligned successfully, with the aligned values.
+Similarly, the rest variables which fail in the alignment are reported in \textit{unaligned}, with their failure reasons.
+
+During the alignment process, RAS first parses the incoming metadata of the two lists according to the provided list formats.
+The current supported list formats are the XML-based response from the WPS's DescribeProcess call and a JSON-based variable template designed for the metadata of random data or varaible from non WPS-implemented models.
+The JSON-based variable template will be described in the next section.
+Then, the two variable lists are resorted according to the criteria that whether a variable in one list is able to be ''matched'' with a variable in another list through semantic mediation in the standard name graph.
+The ''matched'' pairs of variables are used for further alignment, while the ''unmatched'' variables are classified as the \textit{unaligned} in RAS's response.
+The semantic consistency of each pair of the ''matched'' variables is checked in terms of the units, the value type, the temporal and spatial property and the file type.
+The aligning will be conducted if there is any inconsistency based on the given variabl values.
+If the alignment of one pair of variable fail (e.g., conversion from one file type to another is nor supported), then the variables are grouped in the \textit{unaligned} with the reason reported.
+
+A simple applicaiton situation is, for example, that the outputs of a WPS-implemented model A need to be used as the inputs of another WPS-implemented model B.
+The metadata of the two models can be obtained through the WPS DescribeProcess request, say \textit{metadata\_A} and \textit{metadata\_B} respectively.
+The information, which is posted to RAS's service, then includes the following, as shown in Figure \ref{rasWPSIO}:
+\begin{itemize}
+\item the metadata of model A: \textit{metadata\_A}
+\item the format of \textit{metadata\_A}: ''wps output''
+\item the metadata of model B: \textit{metadata\_B}
+\item the format of \textit{metadata\_B}: ''wps input''
+\item the values or URIs of model A's outputs
+\end{itemize}
+After the semantic consistency check and the alignment process, RAS will response back to the client with \textit{aligned} and \textit{unaligned} information in JSON format.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[scale=0.6]{../figures/RASWorkflow.pdf}
+\caption{The workflow of RAS.}
+\label{rasWorkflow}
+\end{figure}
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[scale=0.6]{../figures/RASIO.pdf}
+\caption{An example of the request and the response information of RAS for aligning between the outputs of WPS-implemented model A and the inputs of WPS-implemented model B.
+(Note: the bold texts are implicit information.)}
+\label{rasWPSIO}
+\end{figure}
+
+\subsection{RAS Components} Figure \ref{RASComponents} presents the RAS's components used for the alignment between two lists of variables in terms of  variable name, variable unit, variable value type, file type, variable temporal and spatial properties.
+The alignment is carried out for each pair of variables, say, aligning from variable I to variable II.
+
+\paragraph{variable name} The semantic mediation of two variable names is conducted through either a SKOS-based search or a string-based search.
+SKOS-based search is applied for variable names in a form of URI.
+The procedures are (1) finding all the matched (i.e., \textit{skos:exactMatch} or \textit{skos:closeMatch}) variable names for variable I by querying the standard names graph by using SPARQL\footnote{http://www.w3.org/TR/rdf-sparql-query/}, an Resource Description Framework (RDF) query language; (2) checking whether variable II is in the list of the matched variables of variable I (return matched if true).
+\textit{rdflib}\footnote{https://github.com/RDFLib/rdflib}, a Python library for working with RDF, is utilized for RDF querying.
+In addition, if the types of variable names are string, then the mediation is carried out based on string-based search.
+The variable name in string is first transformed in a URI format by assigning it with a model name space, and then SKOS-based search is used for semantic mediation.
+
+\paragraph{variable unit} Similar to the alignment of two variable names, the conversion of two variable units is based on UDUNITS conversion and SWEET unit conversion, according to the types of units: string and URI, respectively.
+If the unit types are string, UDUNITS\footnote{http://www.unidata.ucar.edu/software/udunits/} (a package support converting units of physical quantities) is employed to perform the conversion.
+On the other hand, a unit ontology of Semantic Web for Earth and Environmental Terminology (SWEET) ontologies is applied in the case that both the unit formats are URI.
+
+\paragraph{variable type} The alignment of the variable types of two variables is based on both the value and file types conversion.
+The value type alignment is straightforward through type conversion in Python (e.g., from \textit{float} to \textit{integer}).
+In terms of conversion in file types, currently the supported file types are comma separated value (CSV) files and Network Common Data Form (NetCDF\footnote{http://www.unidata.ucar.edu/software/netcdf/}) files, with the header information in the file if any.
+
+\paragraph{variable time horizon} The temporal property alignment of two variables is conducted based on linear temporal interpolation, given the start time, the end time and the time step of each variable.
+Through temporal interpolation approach, the actual time period of the data of variable II aligned from that of variable I is the intersection of the given time periods of the two variables.
+It means if the time periods (from the start time to the end time) of the two variables do not overlap, there is no data interpolated for variable II.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[scale=0.7]{../figures/RASComponents} 
+\caption{The components of the Resource Alignment Service (RAS).}
+\label{RASComponents}
+\end{figure}
+
 \section*{References}
